Collision rates of planetesimals near mean-motion resonances

### 2021-01-29 main.tex
Shorten abstract to meet 250 word limit:

\begin{abstract}
\textbf{In circumstellar discs, collisional grinding of planetesimals
  produces second-generation dust. While it remains unclear whether this becomes a major component of the total dust content, 
the presence of such dust and potentially the substructure within it can be used to explore a disc's physical conditions. A perturbing planet produces nonaxisymmetric structures, as
well as gaps in discs, regardless of the origin of the dust. The dynamics of planetesimals, however, will be very different than that of small dust grains due to gas interactions. The
collisional evolution of planetesimals could therefore create dusty disc structures that would not exist otherwise. Previous studies have shown that morphological differences in the
collisional dust corotating with a giant planet can be used to determine whether the planet's eccentricity is large or small. In this work, we use N-body simulations that directly resolve
collisions between planetesimals to investigate the collision rate profile near mean-motion resonances. We  find that a distinct bump or dip feature is produced in the collision profile,
the presence of which depends on the libration width of the resonance and the separation between the peri- and apocenter distances of the edges of the resonance. The presence of
one of these two features limits possible values for the mass and eccentricity of the planet. Under the simplifying assumption that the radial profile of the dust emission in the disc
traces the planetesimal collision profile, we show that the presence of a bump or dip feature in the dust emission near the interior 2:1 mean-motion resonance can be used to place 
constraints on the orbital properties of the perturbing planet. So long as radial drift does not play a significant role in the collisional cascade that grinds planetesimals down to dust, or if 
other processes limit the dust to be approximately local, this feature in the dust emission should be marginally observable in nearby protoplanetary disks with ALMA.}
\end{abstract}

>>>>

\begin{abstract}
\textbf{In circumstellar discs, collisional grinding of planetesimals produces second-generation dust. While it remains unclear whether this ever becomes a major component of the total dust content, the presence of such dust, and potentially the substructure within, it can be used to explore a disc's physical conditions. A perturbing planet produces nonaxisymmetric structures and gaps in the dust, regardless of its origin. The dynamics of planetesimals, however, will be very different than that of small dust grains due to weaker gas interactions. Therefore, planetesimal collisions could create dusty disc structures that would not exist otherwise. In this work, we use N-body simulations to investigate the collision rate profile of planetesimals near mean-motion resonances. We find that a distinct bump or dip feature is produced in the collision profile, the presence of which depends on the libration width of the resonance and the separation between the peri- and apocenter distances of the edges of the resonance. The presence of one of these two features depends on the mass and eccentricity of the planet. Assuming that the radial dust emission traces the planetesimal collision profile, the presence of a bump or dip feature in the dust emission at the 2:1 mean-motion resonance can constrain the orbital properties of the perturbing planet. This assumption is valid, so long as radial drift does not play a significant role during the collisional cascade process. Under this assumption, these features in the dust emission should be marginally observable in nearby protoplanetary disks with ALMA.}
\end{abstract}
